% ========================================
% TÀI LIỆU THAM KHẢO - REFERENCES
% ========================================

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}
\renewcommand{\bibname}{TÀI LIỆU THAM KHẢO}

\begin{thebibliography}{99}

% === 1. Tiêu chuẩn và Giao thức Zigbee ===
\bibitem{zigbee-spec-2023}
Connectivity Standards Alliance. (2023). \textit{Zigbee Specification}. Revision 23. Zigbee Document 05-3474-23.

\bibitem{zigbee-zcl}
Zigbee Alliance. (2019). \textit{Zigbee Cluster Library Specification}. Revision 8. Zigbee Document 07-5123.

\bibitem{silabs-ug103}
Silicon Labs. (n.d.). \textit{UG103.2: Zigbee Fundamentals}. Deprecated version.

% === 2. Tiêu chuẩn và Giao thức MQTT ===
\bibitem{hivemq-mqtt}
HiveMQ. (n.d.). \textit{MQTT Essentials: The Ultimate Guide to the MQTT Protocol for IoT Messaging}. Version 2.0.

\bibitem{emq-mqtt}
EMQ Technologies Inc. (2024). \textit{Mastering MQTT: Your Ultimate Tutorial for MQTT}. Release: R24-3.

\bibitem{mqtt-broker-100}
Gryglecki, M. (HiveMQ). (n.d.). \textit{Speaker Deck: MQTT Broker 100 - Basic}.

% === 3. Giao thức UART ===
\bibitem{uart-adi}
Peña, E., \& Legaspi, M. G. (2020). \textit{UART: A Hardware Communication Protocol - Understanding Universal Asynchronous Receiver/Transmitter}. Analog Devices.

\bibitem{uart-basics}
Circuit Basics. (n.d.). \textit{Basics of UART Communication}.

\bibitem{uart-ti}
Texas Instruments. (2010). \textit{KeyStone Architecture Universal Asynchronous Receiver/Transmitter (UART) User Guide}. Literature Number: SPRUGP1.

% === 4. Tài liệu Phần cứng và Nền tảng (Silicon Labs) ===
\bibitem{silabs-ug261}
Silicon Labs. (n.d.). \textit{UG261: EFR32MG12 2.4 GHz 10 dBm Radio Board User's Guide}. (Dành cho bo mạch BRD4162A và các kit liên quan).

\bibitem{silabs-ug489}
Silicon Labs. (n.d.). \textit{UG489: Silicon Labs Gecko Bootloader User's Guide for GSDK 4.0 and Higher}.

\bibitem{gecko-release-notes}
Silicon Labs. (n.d.). \textit{Gecko Platform Release Notes 4.4.5.0}.

% === 5. NCP / EZSP / Z3Gateway ===
\bibitem{silabs-ezsp}
Silicon Labs. (n.d.). \textit{UG100: EZSP Reference Guide}. EmberZNet Serial Protocol.

\bibitem{silabs-z3gateway}
Silicon Labs. (n.d.). \textit{AN1278: Z3Gateway Example Application}. Zigbee NCP-host gateway using EZSP.

% === 6. Firebase ===
\bibitem{firebase-docs}
Google. (n.d.). \textit{Firebase Documentation}. \url{https://firebase.google.com/docs}.

\bibitem{firebase-rtdb}
Google. (n.d.). \textit{Firebase Realtime Database}. \url{https://firebase.google.com/docs/database}.

% === 7. Flutter ===
\bibitem{flutter-docs}
Google. (n.d.). \textit{Flutter Documentation}. \url{https://docs.flutter.dev}.

% === 8. OTA ===
\bibitem{silabs-ota}
Silicon Labs. (n.d.). \textit{AN728: Over-the-Air Bootload Server and Client Setup}. Zigbee OTA Upgrade Cluster.

\end{thebibliography}
